\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking

### 2013-07-23 jss/article.tex
order

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
             Carl Morris\\ Harvard University\And
             Hyungsuk Tak\\Harvard University }
\title{\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking}

@@

  Carl Morris\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{morris@fas.harvard.edu}\\

  Hyungsuk Tak\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{hyungsuk.tak@gmail.com}\\

}

@@

\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking averages over these indicator variables. We call it a simple unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.

>>>>

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
             Hyungsuk Tak\\Harvard University\And
             Carl Morris\\ Harvard University}
\title{\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking}

@@

  Hyungsuk Tak\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{tak@fas.harvard.edu}\\

  Carl Morris\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{morris@fas.harvard.edu}\\
}

@@

\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking averages over these indicator variables. We call it a simple unbiased coverage probability estimate. For example, $\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.
